```{r}
library(tidyverse)
```

```{r}
library(palmerpenguins)
library(ggthemes)
```

```{r}
penguins
```

```{r}
?mpg
```

```{r}
head(penguins,5)
```

```{r}
tail(penguins,5)
```

```{r}
any(is.na(penguins))
```

```{r}
is.na(penguins)
```

```{r}
colSums(is.na(penguins))
```

```{r}
sum(is.na(penguins))
```

```{r}
glimpse(penguins)
```

```{r}
ggplot(data = penguins,
       mapping = aes(x = flipper_length_mm, y = body_mass_g)) + 
  geom_point(mapping = aes(colour = species, shape = species))+
  geom_smooth(method = "lm")+
  labs(
    title = "Body mass and flipper length",
    subtitle = "Dimensions for Adelie, Chinstrap, and Gentoo Penguins",
    x = "flipper length(mm)", y ="Body mass(g)", 
    colour = "species", shape = "species"
  ) +
  scale_color_colorblind()

```

```{r}
ggplot() + geom_point(
data = penguins,
mapping = aes(x = flipper_length_mm, y = body_mass_g) )+
geom_smooth(
data = penguins,
mapping = aes(x = flipper_length_mm, y = body_mass_g)
)

```

```{r}
penguins |>
  ggplot(aes(x = flipper_length_mm, y = body_mass_g)) +
  geom_point()

```

```{r}
ggplot(penguins, aes(x= species)) + geom_bar()
```

```{r}
ggplot(penguins, aes(x= fct_infreq (species))) + geom_bar()
```

```{r}
ggplot(penguins, aes(x= body_mass_g)) + geom_histogram(bin_width = 200)
```

```{r}
ggplot(penguins, aes(x= body_mass_g)) + geom_density()
ggplot(penguins, aes(colour = species, x = body_mass_g)) + geom_density(linewidth = 0.5)
ggplot(penguins, aes(colour = species,fill = species, x = body_mass_g)) + geom_density(alpha = 0.5)
```

```{r}
ggplot(penguins, aes(x= species, y= body_mass_g)) + geom_boxplot()
```

```{r}
ggplot(penguins, aes(x = body_mass_g)) + geom_density()
```

```{r}
ggplot(penguins, aes(x = species, y = body_mass_g)) +
geom_boxplot()
```

```{r}
ggplot(penguins, aes(x = body_mass_g, color = species)) +
geom_density(linewidth = 0.75)
```

```{r}
ggplot(penguins, aes(x = body_mass_g, color = species, fill = species)) + geom_density(alpha = 0.5)
```

**Two Categorical Variables**

```{r}
ggplot(penguins, aes(x = island, fill = species)) + geom_bar()
```

```{r}
#relative frequency plot
ggplot(penguins, aes(x = island, fill = species)) + geom_bar(position = "fill")
```

**Two Numerical Variables**

```{r}
ggplot(penguins, aes(x = flipper_length_mm, y = body_mass_g)) + geom_point()
```

**Three or More Variables** In the following scatterplot the colors of points represent species, and the shapes of points represent islands

```{r}
ggplot(penguins, aes(x= flipper_length_mm, y= body_mass_g)) +
  geom_point(aes(color= species, shape = island))
```

However, adding too many aesthetic mappings to a plot makes it cluttered and difficult to make sense of. Another option, which is particularly useful for categorical variables, is to split your plot into facets, subplots that each display one subset of the data

The first argument of facet_wrap() which you create with \~ followed by a variable name. The variable that you pass to facet_wrap() should be categorical

```{r}
ggplot(penguins, aes(x= flipper_length_mm, y= body_mass_g)) +
  geom_point(aes(color= species, shape = island)) +
  facet_wrap(~island)
```

**Saving the Plot**

```{r}
ggplot(penguins, aes(x = flipper_length_mm, y = body_mass_g)) + geom_point()
ggsave(filename = "penguin-plot.png")
```
